% !TEX root = main.tex

\chapter{Text Processing}

\section{Spacing problems}
Here is a sum $1+1=2$. Watch the comma $\sum x_n^2$, is there a space? Seems to be fixed!

\subsection*{Non-breaking spaces}
Tildes don't appear in mathmode. Here is an fbox containing lots of them:
\par
\fbox{$A~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~B$}
\par

\bigskip
The {\tt LatexTree} parser replaces
\bit
\it all tildes in normal mode by (non-breaking) spaces and
\it all spaces in mathmode by tildes (to foil Blackboard's rewriters).
\eit


\section{Accents and escaped characters}

\subsection*{Accents}
Spaces between consecutive characters are disappear after processing. This is a consequence of not leaving a space between consecutive text elements. (This can be fixed by merging adjacent text elements, perhaps during post-processing.)
\bit
\it These should be spaced: \'{e} \`{e} \^{w} \"{o} \c{c}.
\it We can manually input the spaces: \'{e}\ \`{e}\ \^{w}\ \"{o}\ \c{c}.
\eit
All seems fine for accented characters inside words:
\bit
\it Cram\'{e}r-Rao.
\it Y m\^{o}r coch.
\it He is blas\'{e} about it.
\eit

\subsection*{Escaped characters}
Here are some escaped characters:
\bit
\it ampersand: \& 
\it percent: \%
\it dollar: \$
\eit

We need to be careful with \$ characters!

\section{Font styles}
Here are some font styles: 
\bit
\it \textbf{bold}
\it \textit{italic}
\it \texttt{teletype}
\it \textsc{small caps} 
\it \textsl{oblique}
\it \emph{emphasis}
\eit

\section{TeX shortcuts for lists}
The itemize macros (\texttt{bit,it,eit}):
\bit
\it apples
\it oranges
\eit

The enumerate macros (\texttt{ben,it,een}):
\ben
\it first
\it second
\een

{\tt LatexTree} deals with these during pre-processing.

